A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)

### 2018-04-12 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

\bigskip
This work focuses on reducing the order of permeability field distribution for multiphase flow simulations in porous media. Section~\ref{section:mathematical_model} presents the mathematical model used to describe the relevant physics for multi-fluid flow through porous media and highlights the relevance of the permeability field. The mathematical model is discretised by a novel high-order accurate control volume finite element method (CVFEM) which couples both the fine resolution and upscaled representation of the permeability field. Pre-processing statistical properties and post-simulation multiphase flow behaviour are investigated to analyse the various upscaling techniques used.

>>>>

\bigskip
This work focuses on reducing the order of permeability field distribution for multiphase flow simulations in porous media. Section~\ref{section:mathematical_model} presents the mathematical model used to describe the relevant physics for multi-fluid flow through porous media and highlights the relevance of the permeability field. The mathematical model is discretised by a novel high-order accurate control volume finite element method (CVFEM) \cite{gomes_2017} which couples both the fine resolution and upscaled representation of the permeability field. Pre-processing statistical properties and post-simulation multiphase flow behaviour are investigated to assess the various upscaling techniques used.
